% resume.tex


\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large
\colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1
\vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
               \textbf{#1} & #2 \\
               \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Steven MacCoun}   & (720) 891-2715\\
9231 Crestmore Way  & steven.maccoun@colorado.edu \\
Littleton, CO 80126& \\
\end{tabular*}
\\

\vspace{0.1in}

{\bf Objective:} Meow Mix Please Deliver

\resheading{Education}
\begin{itemize}
\item
       \ressubheading{University of Colorado Graduate School}{Boulder,
CO}{Master's Candidate: Computer Science}{Beginning fall 2011}
   
\item
       \ressubheading{University of Colorado}{Boulder, CO}{BA
Physics}{Sept. 2006 - May 2011}
       \begin{itemize}
               \resitem{Cumulative GPA: 3.4}
               \resitem{Courses Completed in Computer Science include:}
       \end{itemize}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
       \ressubheading{Physics Undergraduate Research}{Nuclear Physics Laboratory}{Research Assistant, 15 hours/week}{Jan. 2010 - Sept. 2010}
       \begin{itemize}
               \resitem{Helped in constructing and designing aspects of detector to be built for Fermilab}
               \resitem{Responsible for researching and gathering appropriate materials to fit design principles}
               \resitem{Certified for machine shop}
       \end{itemize}

\item
       \ressubheading{Undergraduate TA}{University of Colorado}{Learning Assistant, 10 hours/week}{Jan. 2009 - May. 2009}
       \begin{itemize}
               \resitem{Faciliated problem solving techniques among groups of 4-6 students in introductory physics}
               \resitem{Developed effective ways to handle small group dynamics}
       \end{itemize}

\item
       \ressubheading{Physics Tutor}{CU ASAP Program}{Mechanics/EM Tutor, 10 hours/week}{Feb. 2010 - Current}
       \begin{itemize}
               \resitem{Applied knowledge of mechanics and electricity and magnetism to aid student understanding}
               \resitem{Enhanced personal pedagogical and team management skills for working in small groups}
       \end{itemize}

\item
       \ressubheading{ER Assistance}{Swedish Hospital}{Patient Transporter, 40 hours/week}{May 2007 - Aug. 2007}
       \begin{itemize}
               \resitem{Managed several tasks in a busy ER}
               \resitem{Worked well with patients and nurses}
       \end{itemize}
\end{itemize}

\resheading{Awards}

\begin{description}
\item[Noyce Fellowship] \emph{Awarded 2009} 10,000 dollar scholarship. Performed research in undergraduate physics education.

\end{description}

\resheading{Skills \& Interests}

\begin{description}
\item[Languages:] C/C++, Python
\item[API:] OpenGL
\item[Software:] Maya
\item[Debugger:] Eclipse
\end{description}

\end{document}
